\section{Modelling Secondary Education in PDDL}
This project employs a structured ontology in PDDL, encompassing types, constants, and predicates to model secondary education. Types include courses, course levels, weeks, units, extracurricular activities, grades, preferred learning styles, and student support requirements. Constants consist of strategies, school calendar weeks, units, extracurricular activities, predicted grades, and student preferences and support requirements. Predicates establish relationships such as finished courses, course enrollment, predicted grades, completion of weeks, units, and extracurricular activities, participation in study groups, adoption of learning strategies, identification of support needs, and provision of support.

\subsection{LEARNS Architecture}
Planning learning paths for students requires the initial step of creating a framework, which is one that contains 36 weeks. There are $32$ weeks for learning, and $4$ weeks for students to be assessed by means of unit tests. There are also a number of variables to consider, such as a student (\texttt{?s}), the course they are sitting (\texttt{?c}), the level of the course (\texttt{?l}), what grade they are expected to achieve in a given course (\texttt{?g}), what week they are currently on (\texttt{?w}), what unit they are achieving on (\texttt{?u}), what extracurricular activity they are doing (\texttt{?e}), what learning strategy they prefer (\texttt{?t}), and what support requirements they may have (\texttt{?r}). These variables are used to aid in the guidance of students through this learning recognition system.

The successful completion of each week is systematically recorded through the \texttt{done-week} predicate, as denoted in Figures~\ref{fig:do-week-one} and~\ref{fig:do-week-n}. Figure~\ref{fig:do-week-n} is an action that is chained from Figure~\ref{fig:do-week-one}, and is executed for each week that is to be completed (week-n), $n$ is in the range of $2 \leq n \leq 8$ and represents the weeks $2$ through $8$ respectively. This is formalised in Figures~\ref{fig:do-week-one} and~\ref{fig:do-week-n}.

\input{figures/tex/actions/week-one.tex}
\input{figures/tex/actions/week-n.tex}

After eight weeks have passed, students are provided with a unit test to complete. The \texttt{done-unit} predicate in Figures~\ref{fig:take-unit-one} and~\ref{fig:take-unit-n} denote their passing of the unit \textemdash~assuming that all students who take a unit will pass it. This is a simplification of the problem, as it is possible for students to fail a unit test. However, this is not a concern for this project, as the focus is on the planning of learning paths, rather than the planning of resits. Following the accomplishment of a unit, students are then tasked with a subsequent 8-week cycle, this cycle persists until the student has completed all four units from the course.

\input{figures/tex/actions/unit-one.tex}
\input{figures/tex/actions/unit-n.tex}

A student has completed a course when all four units are complete, and is denoted by the \texttt{finished-course} predicate. Figure~\ref{fig:finish-course} provides the action to check that the student has completed the course. This is a prerequisite for the student to be able to take the final exam \textemdash~of which is not monitored by this system, as it is an application of automated planning to generate learning paths for students with additional support requirements, not for handling the logistics of the school.

\input{figures/tex/actions/finished-course.tex}

Alongside their academics, extracurricular activities play a vital role in student development. For each unit, students can participate in two extracurricular activities. Grade-a students are expected to commit to both, while grade-b students typically commit to one. Figures~\ref{fig:extra-curricular-one} and~\ref{fig:extra-curricular-n} illustrate this academic involvement, highlighting the sequential nature of these activities.

\input{figures/tex/actions/ec-one.tex}
\input{figures/tex/actions/ec-n.tex}

Extracurricular activities alternate, starting with \texttt{do-extra-curricular-one} and progressing to \texttt{do-extra-curricular-n}. This pattern repeats for each unit, and completion is indicated by the \texttt{done-extra-curricular} predicate. The approximation stems from the earlier statement that grade-a or grade-b students may engage in either one or two extracurricular activities. However, this simplification overlooks the possibility of non-grade-a or non-grade-b students participating and grade-a or grade-b students deviating from the specified number of extracurricular engagements. This system is designed to provide recommendations to aid in the planning of learning paths, not to handle the logistics of the school.

Students willing to engage in collaborative group dynamics can participate in group-oriented extracurricular activities. This collaboration is depicted in Figures~\ref{fig:team-extra-curricular-one} and~\ref{fig:team-extra-curricular-n}, illustrating the synergistic environment fostered through teamwork in extracurricular pursuits.

\input{figures/tex/actions/team-ec-one.tex}
\input{figures/tex/actions/team-ec-n.tex}

\subsection{Support Structures}
Through our independent research, we have identified that students grappling with communication challenges can benefit significantly from specialised workshops aimed at enhancing their skills. This provision is particularly pertinent for students facing social issues, those on the autism spectrum, or individuals with linguistic difficulties. Moreover, students who prefer specific learning styles, such as teamwork, project-based learning, or blended learning for those unable to attend physical school, can find valuable support in communication improvement workshops. Figure~\ref{fig:improve-comms-workshop} illustrates the relevance and potential impact of these workshops.

\input{figures/tex/actions/improving-comms-workshop.tex}

For students encountering difficulties in reading or those who could benefit from tools like audiobooks, we offer a dedicated reading group workshop. The details of this initiative are outlined in Figure~\ref{fig:reading-group}, providing a comprehensive understanding of the resources and strategies employed to assist students in enhancing their reading abilities.

\input{figures/tex/actions/reading-group-workshop.tex}

Recognising the diverse needs of our student population, we acknowledge the significance of technology-assisted learning. We are equipped to provide students with tailored tools to support their learning journeys. This could be especially beneficial for students on the autism spectrum, facing language difficulties, experiencing profound deafness or hearing impairments, those with visual impairments, or individuals who simply prefer leveraging technology for their educational pursuits. Figure~\ref{fig:tech-assist} offers an insight into the specifics of our approach in this domain.

\input{figures/tex/actions/tech-assistance.tex}

Furthermore, we understand that some students may derive greater benefits from breaking their study time into smaller, focused intervals. Embracing the Pomodoro technique, students can optimise their learning experiences by strategically dividing their study sessions. Figure~\ref{fig:pomo-study} provides a detailed illustration of how this technique can be applied to enhance learning outcomes.

\input{figures/tex/actions/pomodoro-study.tex}